---
title: "A bit of git-ting"
subtitle: |
  Create and delete repo
author: Pratik Bhandari
date: 2021-08-12
categories:
  - codes
  - bash
  - git
  - version control
  - germany
  - "2021"
---

<!-- Hide the preview -->

The first thing that I do for any data analyses or writing project is create a remote git repository either in github or in gitlab. Then I create a local R project in R Studio, and connect it to the remote git repo. The 'how-to' of this process can be found online; I'll write up a brief overview, probably.

This post is to remind myself of most frequently used git commands.

<!-- When you click on 'New Project' on the top right drop down menu, R Studio give you three choices and one of them is to *Checkout a project from a version control repository*.-->

```{r branching}
#| eval: false
#| echo: true
# Push local changes to the remote repo:
git push -u origin master

# Creat and checkout new branch:
git checkout -b NewBranchName

git push -u origin BranchIamWorkingOn # to push from local repo to remote repo if the remote repo doesn't have this `BranchIamWorkinOn` setup up already

# Delete a local branch:
git branch -D BranchToBeDeleted
```
Be careful on deleting. The `-D` is a hard delete! 


Merge branches locally:

```{r merging}
#| eval: false
#| echo: true
git checkout main #First switch to the main/master branch
git merge BranchIwantToMerge #The branch still exists after merging
```

This was a dirty note down as I frequently make mistakes using these commands. `git pull`, `git merge`, etc. are also used but not much problematically.

Tune in for more frequently used `R` and `bash` scripts :D
